Preliminary Draft

### 2021-07-22 article/draft.tex
ignored uneeded files

Furthermore, mainstream platforms are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see table \ref{summary} in Appendix \ref{links}). While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation. The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense. \footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.}

@@

Hence, in the present article, we focus on mainstream platforms' policies and interventions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (see Lazer et al. (2018)~\cite{lazer}). The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.  The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network. Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for YouTube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see table \ref{summary} in Appendix \ref{links}).

@@

During the COVID-19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}). Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc. As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines (as of July 2021). The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report}''. %Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).

@@

\begin{table}[h]
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
with no flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check and an \\  information flags\end{tabular} \\ \hline
0            & 7                        & 4                      & 7                                                                                     \\ \hline
\end{tabular}
\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
\label{tab_flags_fb}
\end{table}

@@

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.29]{./img/youtube_panels/yt_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.294]{./img/youtube_panels/yt_3.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_4.png} 
	%\end{multicols}
	\caption{Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}. }
	\label{fig9}
\end{figure}
%Nevertheless, we noticed that duplicates of the same YouTube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.

>>>>

Furthermore, mainstream platforms are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and YouTube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see Appendix \ref{links} for references). While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation. The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense. \footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation.}

@@

Hence, in the present article, we focus on mainstream platforms' policies and interventions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (see Lazer et al. (2018)~\cite{lazer}). The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.  The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network. Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for YouTube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see Appendix \ref{links} for references).

@@

During the COVID-19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see Appendix \ref{links} for references). Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged, suspending accounts, implementing strike systems, reducing the visibility of content, etc. As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines (as of July 2021). The 2019 report of the Facebook Data Transparency Advisory Group (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report}''. %Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom. Similarly, Twitter communicates about actions related to misinformation via their \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{Twitter Safety} Blog/account. In a post on YouTube Official Blog, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation (see table \ref{summary} in Appendix \ref{links}).

@@

\begin{table}[h]
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
without a flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check and an \\  information flags\end{tabular} \\ \hline
0            & 7                        & 4                      & 7                                                                                     \\ \hline
\end{tabular}
\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
\label{tab_flags_fb}
\end{table}

@@

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.29]{./img/youtube_panels/yt_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.294]{./img/youtube_panels/yt_3.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_4.png} 
	%\end{multicols}
	\caption{Screenshots taken on July 21, 2021. Examples of YouTube information panels displayed under Youtube videos respectively about: \href{https://www.youtube.com/watch?v=OwqIy8Ikv-c}{Climate change}, \href{https://www.youtube.com/watch?v=9sW0OmzcmL0}{COVID-19 Vaccine}, \href{https://www.youtube.com/watch?v=usyQgPU-VrI}{COVID-19} and \href{https://www.youtube.com/watch?v=8PAwc8nlE\_Q}{US elections}. }
	\label{fig9}
\end{figure}
%Nevertheless, we noticed that duplicates of the same YouTube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all.
